---
title: "High impact mutations drive DNA methylation variation after colonization of a novel habitat"
author: "Johan Zicola"
date: "`r format(Sys.time())`"
output:
  github_document:
    toc: true
  html_notebook:
    toc: true
  pdf_document:
    toc: true
  html_document:
    toc: true
    df_print: paged
documentclass: article
classoption: a4paper
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

```{r,echo=FALSE,message=FALSE,warning=FALSE}
# Set so that long lines in R will be wrapped:
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 80), tidy = TRUE)
```


# Description

This repository contains the bioinformatic analysis of the paper Zicola et al.


# Phenotypic analysis growth chamber

## R libraries

```{r}

```




# Phenotypic analysis field trials

## R libraries

```{r}

```

# RNA-seq analysis

## R libraries

```{r}

```

# sRNA-seq analysis




# Degradome analysis

## R libraries

```{r}

```



# Author

* **Johan Zicola** - [johanzi](https://github.com/johanzi)

# License

This project is licensed under the MIT License - see the [LICENSE](LICENSE) file for details


